CLT Results

### 2022-04-03 analysis/clt_data_processing.Rmd
update data

ggplot(p2, aes(x = age, y = mean))+
  #stat_cor()+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = .75)+
  #geom_point( alpha = .75)+
  geom_smooth(method = "lm")+
  labs(x = "Age", y = "Proportion correct")+
  ylim(0,1)+
  xlim(3,8.2)+
  theme_minimal()
```

>>>>

ggplot(p2, aes(x = age, y = mean))+
  #stat_cor()+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = .25)+
  #geom_point( alpha = .75)+
  geom_smooth(method = "lm")+
  labs(x = "Age", y = "Proportion correct")+
  ylim(0,1)+
  xlim(3,8.2)+
  theme_minimal()
```
